\Large \bf Security Audit of Safeplug ``Tor in a Box''

### 2014-07-16 foci/paper.tex
Anna hopefully final edits. Particularly section 5.4

\subsection{Information Prior to Using the Device: Terms of Service}
\label{tos}
The TOS are never presented to the user: they aren't presented in the Safeplug package or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.

@@

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
\label{table_example}
\centering
\small
	\begin{tabular}{|c|c|}
	\hline
		Platform & Browsers \\ \hline
		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
		OSX & Safari, Chrome, Firefox \\ \hline
		iOS	& Safari \\ \hline
		Android	& Chrome \\ \hline
	\end{tabular}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=.5\textwidth]{settings_with_exit}
  \caption{Safeplug settings page.  The last button ``Allow Exit'' only appears if the relay option above has been turned on.}
  \label{fig:settings}
\end{figure}

@@

Although Safeplug has a warning about clearing cookies on their FAQ page, it only mentions clearing cookies after a browser session.  Of greater concern would be tracking a user during their browser session from website to website; preventing this requires knowledge and vigilance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.

@@

\section{Privoxy vs. Tor Browser Bundle}
The Safeplug uses two primary technologies: Tor and Privoxy.  The Tor Project has developed the Tor Browser Bundle, which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.  A differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy.  We ran a privacy study on the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.  All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, JavaScript objects, flash objects, and third party cookies.  Because measuring privacy is a difficult task, we measured potential ways for a user's privacy to be compromised.  First, we recorded how many third party domains were accessed total (throughout the crawl); in addition, we recorded the total number of JavaScript and Flash objects received from third parties, as well as the total number of third party cookies received.  We then found the on-average, per-page numbers corresponding to these measurements by dividing the totals by 100.  These fractions are shown in Table~\ref{tbb}.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the average number of Third Party Domains accessed per page, the average number of Javascript objects received from third parties per page, the average number of Flash objects received from third parties per page, and the average number of third party cookies received per page.}
\label{tbb}
\centering
\small
	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
	\hline
		Configuration & Third Party Domains & Third Party JavaScript & Third Party Flash & Third Party Cookies \\ \hline
		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
		Privoxy & 0.72 & 0.00 & 0.01 & 0.84 \\ \hline
		Tor Browser	& 0.58 & 0.01 & 0.00 & 0.00 \\ \hline
	\end{tabular}
\end{table}

@@

\subsection{Spoofing the Update Server}
\label{dnsspoof}
An additional dangerous class of vulnerabilities comes from the lack of HTTPS during the software update process.  We discovered that the update script is downloaded via TCP from an IP address provided by the Pogoplug servers.  This update script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the update script itself.  An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious update script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.  Because the activation occurs over TCP rather than anything more secure, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.  This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.

@@

\subsection{Opportunities}
Despite all the structural problems, is there a market for a Torifying piece of hardware?  Given the security pitfalls in comparison to a piece of software such as the Tor Browser Bundle, there seems to be no reason for a user who can run the Tor Browser Bundle to purchase the Safeplug or any other device.  For mobile phones, the proxy problems with mobility contribute to an already high usability cost.  However, there are an emerging class of ``smart home'' devices which may connect to the Internet.  It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.  For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?  Since the data sent by these devices to the service provider likely contains identifying information, the use of Tor would only protect the user's location at the expense of connection time and load on the Tor network.  Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy is of questionable value in this space as well.

>>>>

\subsection{Information Prior to Using the Device: Terms of Service}
\label{tos}
The Terms of Service (TOS) are never presented to the user: they aren't presented in the Safeplug package or shown during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.

@@

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\centering
\small
	\begin{tabular}{|c|c|}
	\hline
		Platform & Browsers \\ \hline
		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
		OSX & Safari, Chrome, Firefox \\ \hline
		iOS	& Safari \\ \hline
		Android	& Chrome \\ \hline
	\end{tabular}
\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
\label{table_example}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=.5\textwidth]{settings_with_exit}
  \caption{Safeplug settings page.  The last button ``Allow Exits'' only appears if the relay option above has been turned on.}
  \label{fig:settings}
\end{figure}

@@

Although Safeplug has a warning about clearing cookies on their FAQ page, it only mentions clearing cookies after a browser session.  This does not prevent the tracking of a user during their browser session from website to website; preventing this requires knowledge and vigilance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.

@@

\section{Privoxy vs. Tor Browser Bundle}
The Safeplug uses two primary technologies: Tor and Privoxy.  The Tor Project has developed the Tor Browser Bundle (TBB), which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.  A differentiating factor between the Safeplug and the TBB is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy against the other features of the TBB.  We ran a privacy study on the use of Firefox, Firefox with Privoxy, and the TBB; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.  All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, JavaScript objects, flash objects, and third party cookies.  Because measuring privacy is a difficult task, we measured potential ways for a user's privacy to be compromised.  First, we recorded how many third party domains were accessed total (throughout the crawl); in addition, we recorded the total number of JavaScript and Flash objects received from third parties, as well as the total number of third party cookies received.  We then found the on-average, per-page numbers corresponding to these measurements by dividing the totals by 100.  These fractions are shown in Table~\ref{tbb}.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\centering
\small
	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
	\hline
		Configuration & Third Party Domains & Third Party JavaScript & Third Party Flash & Third Party Cookies \\ \hline
		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
		Privoxy & 0.72 & 0.00 & 0.01 & 0.84 \\ \hline
		Tor Browser	& 0.58 & 0.01 & 0.00 & 0.00 \\ \hline
	\end{tabular}
\caption{Measurements of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the average number of Third Party Domains accessed per page, the average number of Javascript objects received from third parties per page, the average number of Flash objects received from third parties per page, and the average number of third party cookies received per page.}
\label{tbb}
\end{table}

@@

\subsection{Spoofing the Installation Server}
\label{dnsspoof}
An additional dangerous class of vulnerabilities comes from the lack of HTTPS during the initial installation process.  We discovered that the script that performs this installation is downloaded via TCP from an IP address provided by the Pogoplug servers.  This script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the script itself.  An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.  Because the activation occurs over TCP, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.  This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.  Note: We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process DOES occur over HTTPS.

@@

\subsection{Opportunities}
Despite all the structural problems, is there a market for a Torifying piece of hardware?  Given the security and privacy pitfalls in comparison to a piece of software such as the Tor Browser Bundle, there seems to be no reason for a user who can run the Tor Browser Bundle to purchase the Safeplug or any other device.  For mobile phones, the proxy problems with mobility contribute to an already high usability cost.  However, there are an emerging class of ``smart home'' devices which may connect to the Internet.  It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.  For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?  Since the data sent by these devices to the service provider likely contains identifying information, the use of Tor would only protect the user's location at the expense of connection time and load on the Tor network.  Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy is of questionable value in this space as well.
